CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-06-06 script/en/chapters/aboutcryptool.tex
fixes for beta6
be update

\parskip 4pt
%\vskip +12 pt
{
\noindent In this CrypTool\index{CrypTool} script you will find predominantly
mathematically oriented information on using cryptographic procedures.
The main chapters have been written by {\em various authors} and are
therefore independent from one another. At the end of most chapters
you will find literature and web links.

@@

The {\em authors} Bernhard Esslinger, Matthias B\"uger, Bartol Filipovic, 
Henrik Koy, Roger Oyono and J\"org-Cornelius Schneider
would like to take this opportunity to thank their colleagues 
in the company and at the universities of Frankfurt, Gie\ss en, 
Siegen, Karlsruhe and Darmstadt. They are particularly indepted to Dr.~Peer
Wichmann from the Karlsruhe computer science research centre (Forschungszentrum
Informatik, FZI) for his down-to-earth support.

>>>>

\parskip 4pt
%\vskip +12 pt
{
\noindent In this CrypTool\index{CrypTool} script you will find predominantly
mathematically oriented information on using cryptographic procedures.
The main chapters have been written by various
\hyperlink{appendix-authors}{authors}
(see appendix \ref{s:appendix-authors})
and are therefore independent from one another. At the end of most chapters
you will find literature and web links.

@@

The authors Bernhard Esslinger, Matthias B\"uger, Bartol Filipovic, 
Henrik Koy, Roger Oyono and J\"org Cornelius Schneider
would like to take this opportunity to thank their colleagues 
in the company and at the universities of Frankfurt, Gie\ss en, 
Siegen, Karlsruhe and Darmstadt. They are particularly indepted to Dr.~Peer
Wichmann from the Karlsruhe computer science research centre (Forschungszentrum
Informatik, FZI) for his down-to-earth support.

### 2003-06-06 script/en/chapters/authors.tex
fixes for beta6
be update

\section{Authors of this script}
This appendix lists the authors of this document. Please refer to the top of the individual
chapters for their contribution.

\begin{description}
\item[Bernhard Esslinger,] initiator of CrypTool, head IT security at Deutsche
Bank and lecturer on IT security at the University of Siegen.

>>>>

\section{Authors of this script}
\hypertarget{appendix-authors}{}\label{s:appendix-authors}
This appendix lists the authors of this document. Please refer to the top of the individual
chapters for their contribution.

\begin{description}
\item[Bernhard Esslinger,] initiator of the CrypTool project, head IT security
at Deutsche Bank and lecturer on IT security at the University of Siegen.
E-mail: besslinger@web.de.

### 2003-06-06 script/en/chapters/ellipticcurves.tex
be update

If the characteristic is finite, it has to be prime. This fact can easily be proved: Assume $n=pq$, $p,q<n$, is the characteristic of a field $K$. By definition of $n$, the elements $\bar p=\underbrace{1+1+\dots+1}_{\hbox{$p$ times}}$, $\bar q=\underbrace{1+1+\dots+1}_{\hbox{$q$ times}}$ of $K$ are not equal to $0$. Thus, there exist inverse elements $\bar p^{-1},\bar q^{-1}$ with respect to multiplication. It follows that $(\bar p\bar q)( $\bar p^{-1}\bar q^{-1})=1$, which contradicts the fact that $\bar p\bar q=\bar n=\underbrace{1+1+\dots+1}_{\hbox{$n$ times}}=0$ and, hence, $\underbrace{(\bar p\bar q)}_{=0}( $\bar p^{-1}\bar q^{-1})=0$.

@@

This problem is known as the \glqq over Elliptic Curve Discrete Logarithm Problem \grqq\ (for short ECDLP\index{ECDLP}).

@@

\bibitem[Lenstra1987]{Lenstra1987} H.W. Lenstra\\ \index{Lenstra 1987}
   Factoring integers with elliptic curves, 
   Annals of Mathematics 126, pp. 649-673, 1987.

\end{thebibliography}

>>>>

If the characteristic is finite, it has to be prime. This fact can easily be proved: Assume $n=pq$, $p,q<n$, is the characteristic of a field $K$. By definition of $n$, the elements $\bar p=\underbrace{1+1+\dots+1}_{\hbox{$p$ times}}$, $\bar q=\underbrace{1+1+\dots+1}_{\hbox{$q$ times}}$ of $K$ are not equal to $0$. Thus, there exist inverse elements $\bar p^{-1},\bar q^{-1}$ with respect to multiplication. It follows that $(\bar p\bar q)(\bar p^{-1}\bar q^{-1})=1$, which contradicts the fact that $\bar p\bar q=\bar n=\underbrace{1+1+\dots+1}_{\hbox{$n$ times}}=0$ and, hence, $\underbrace{(\bar p\bar q)}_{=0}(\bar p^{-1}\bar q^{-1})=0$.

@@

This problem is known as the ``over Elliptic Curve Discrete Logarithm Problem'' (for short ECDLP\index{ECDLP}).

@@

\bibitem[Lenstra1987]{Lenstra1987} H.W. Lenstra\\ \index{Lenstra 1987}
   Factoring integers with elliptic curves, 
   Annals of Mathematics 126, pp. 649-673, 1987.
\end{thebibliography}

### 2003-06-06 script/en/chapters/moderncryptography.tex
be update

The term ``practically impossible'' is slightly less precise. In 
general, we can say that a problem cannot be solved \index{Runtime!efficient} 
efficiently, if the time required to solve it increases more quickly than the 
polynomial \index{Polynomial }time as a function of the size of the input. If, for example, the 
length of the input is $ n $  bits and the time required for calculating the 
function is proportional to $ 2^n $, then the following currently applies: the 
function practically cannot be calculated for $n > 80$.

>>>>

The term ``practically impossible'' is slightly less precise. In 
general, we can say that a problem cannot be solved \index{Runtime!efficient} 
efficiently, if the time required to solve it increases more quickly than the 
polynomial\index{Polynomial} time as a function of the size of the input. If, for example, the 
length of the input is $ n $  bits and the time required for calculating the 
function is proportional to $ 2^n $, then the following currently applies: the 
function practically cannot be calculated for $n > 80$.
